\cvsection{Projects}
\begin{cventries}
  \cventry
    {Android - Java \enskip\cdotp\enskip Express - Node.js \enskip\cdotp\enskip PostgreSQL}
    {Cafeteria Franchising Terminal}
    {Mobile Computing Course}
    {Sep. 2016 - Feb. 2017}
    {
      \begin{cvitems}
        \item {This project consists in the development of two independent applications for Android devices.}
        \item{The client-side applications allows clients to buy anything they want and after that a QR code is generated to be presented in the Cafeteria terminal application which is responsible to make all the payment process through the client credit-card number.}
        \item{An API was implemented to make easier the control of all transactions and operations. Both client-side and terminal application can communicate with it. When the server is offline, the application are implemented to communicate with it when the connection establishes again. }
      \end{cvitems}
    }
    
    \cventry
    {C\# - Xamarim \enskip\cdotp\enskip SQLite}
    {Currency Converter}
    {Mobile Computing Course}
    {Sep. 2016 - Feb. 2017}
    {
      \begin{cvitems}
        \item {This project consists in the development native application for Android and Windows devices using the cross-platform Xamarim.}
        \item{The goal of the application is to support users regarding the conversion of different currencies (e.g. euros to dollars).}
        \item{The application updates, when possible, the current value of every currency when it starts through the Yahoo Finance API.}
      \end{cvitems}
    }
    
  \cventry
    {jQuery \enskip\cdotp\enskip Java \enskip\cdotp\enskip ANTLR}
    {JjQuery}
    {Compilers Course}
    {Feb. 2015 - Jul. 2015}
    {
      \begin{cvitems}
        \item {A tool implemented to translate valid jQuery selectors into executable Java code.}
        \item{ANTLR was used to help in the development of lexical, syntactic and semantic representation functions to translate the code.}
      \end{cvitems}
    }
    \cventry
    {VDM++ \enskip\cdotp\enskip Java}
    {Mastermind}
    {Formal Methods in Soft. Eng. Course}
    {Sep. 2015 - Feb. 2016}
    {
      \begin{cvitems}
        \item {Mastermind, a board game, was implemented using Vienna Development Method (VDM++) to validate all the operations and objects that will constitute the source-code in a Java version.}
      \end{cvitems}
    }
    
    \cventry
    {C\# - .NET \enskip\cdotp\enskip HTML5 \enskip\cdotp\enskip CSS3 \enskip\cdotp\enskip Microsoft SQL Server}
    {Dashboard360}
    {Information Systems Course}
    {Sep. 2015 - Feb. 2016}
    {
      \begin{cvitems}
        \item {Dashboard360 is a tool that allows companies to see the overall statistics of its businesses. This tool needs to be connected to an ERP Primavera to get all the necessary information to build the visual representations.}
      \end{cvitems}
    }
    
    \cventry
    {PHP \enskip\cdotp\enskip HTML5 \enskip\cdotp\enskip CSS3 \enskip\cdotp\enskip SQLite}
    {PollHub}
    {Web Lang. and Technologies Course}
    {Sep. 2015 - Feb. 2016}
    {
      \begin{cvitems}
        \item {PollHub is a website where people can create polls quickly and invite others to participate.}
      \end{cvitems}
    }
    
    \cventry
    {PHP - Smarty \enskip\cdotp\enskip HTML5 \enskip\cdotp\enskip CSS3 \enskip\cdotp\enskip PostgreSQL}
    {AskFEUP}
    {Database \& Web Apps. Lab. Course}
    {Feb. 2015 - Jul. 2015}
    {
      \begin{cvitems}
        \item {AskFEUP is a Q\&A platform built using the template engine Smarty. Users can create, answer, comment and classify questions as well as its respective answers.}
      \end{cvitems}
    }
    
    \cventry
    {C++ \enskip\cdotp\enskip Prolog \enskip\cdotp\enskip OpenGL}
    {Eximo}
    {Graphical Applications Lab. Course}
    {Sep. 2014 - Feb. 2015}
    {
      \begin{cvitems}
        \item {Eximo is a board game with a 3D visualiser client developed in C++/OpenGL and the whole game logic is in charge of a Prolog server.}
      \end{cvitems}
    }
     
\end{cventries}
